Quality measure notes

### 2021-07-14 StateOfPractice/Ao-Report/13Methods.tex
ao report - ch 3 minor update

Among the 48 software packages, there were several ones that we could not find in their source code, such as \textit{MicroDicom}, \textit{Aliza}, and \textit{jivex}, etc. These packages are likely to be freeware defined in Section \ref{sec_freeware} and not OSS. So following guidelines in Section \ref{sec_filter_software_list} we removed them from the list. Next, we focused on the MI software that could work as a MI viewer. Some of the software on the list were tool kits or libraries for other software to use as dependencies but not for end-users to view medical images, such as \textit{VTK}, \textit{ITK}, \textit{dcm4che}, etc. We also eliminated these from the list. After that, there were 29 software products left on the list. We still preferred projects using git and GitHub and being updated recently, but did not apply another filtering since the number of packages was already below 30. However, 27 out of the 29 software packages on the final list used git, and 24 chose GitHub. Furthermore, 27 packages had the latest updates after the year 2018, and 23 after 2020.

>>>>

Appendix \ref{ap_list_before_filtering} shows all the 48 software packages. Among them, there were several ones that we could not find in their source code, such as \textit{MicroDicom}, \textit{Aliza}, and \textit{jivex}, etc. These packages are likely to be freeware defined in Section \ref{sec_freeware} and not OSS. So following guidelines in Section \ref{sec_filter_software_list} we removed them from the list. Next, we focused on the MI software that could work as a MI viewer. Some of the software on the list were tool kits or libraries for other software to use as dependencies but not for end-users to view medical images, such as \textit{VTK}, \textit{ITK}, \textit{dcm4che}, etc. We also eliminated these from the list. After that, there were 29 software products left on the list. We still preferred projects using git and GitHub and being updated recently, but did not apply another filtering since the number of packages was already below 30. However, 27 out of the 29 software packages on the final list used git, and 24 chose GitHub. Furthermore, 27 packages had the latest updates after the year 2018, and 23 after 2020.
